\documentclass[11pt]{article}

%defines page size and margins
\usepackage{geometry}
\geometry{
    letterpaper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

%Sets spacing for entire document
\usepackage{setspace}
\doublespacing

%Package for reducing space in between list items
\usepackage{enumitem}

%Math symbols
\usepackage{gensymb}

%Links n shit
\usepackage{hyperref}

%dope tables
\usepackage{array}
\usepackage{float}

%Image path
\usepackage{graphicx}
\graphicspath{ {../Images/} }

%Makes lists easier
\newcommand{\ol}[1]{\begin{enumerate}[noitemsep, topsep=0pt]#1\end{enumerate}}
\newcommand{\ul}[1]{\begin{itemize}[noitemsep, topsep=0pt]#1\end{itemize}}
\newcommand{\li}[1]{\item#1}

%Bibliography
\newenvironment{bib}[1]
  {\begin{list}
          {}
          {\setlength{\itemindent}{-#1}
           \setlength{\leftmargin}{#1}
           \setlength{\itemsep}{0pt}
           \setlength{\parsep}{\parskip}
           \setlength{\topsep}{\parskip}
           }
    \setlength{\parindent}{-#1}
    \item[]
  }
  {\end{list}}

\begin{document}
\singlespacing
{\Large\noindent Rishabh Shah

\noindent 4655 4192

\noindent October 25, 2017

\noindent Museums 301 Midterm Question Three}

\subsection*{The film \textit{Robbing the Cradle of Civilization}, about the 2003 looting of the Iraqi National Museum, provides a case study for exploring ethical issues surrounding ownership and care of the world’s cultural heritage. According to this film, who are the ``major players'' in the world’s antiquities market and what motivates each of these groups to participate? Specifically, what role do museums play in this network? Finally, in your opinion, which of these groups is ultimately responsible for ``robbing the cradle of civilization''? Use specific examples from the film, class readings, or lectures to support your answer.}

\doublespacing
When the United States led coalition invaded Iraq in 2003, it was the beginning of a long and bloody conflict that still continues today. The invasion was largely based on the claim that Iraq was in possession of weapons of mass destruction, along with the goal of freeing the Iraqi people. The invasion began in mid-March of 2003 and coalition forces quickly reached and captured the capital Baghdad by early-April.\footnote{``Iraq War 2003-2011,'' \textit{Britannica}, accessed October 24, 2017, \url{https://www.britannica.com/event/Iraq-War}.} During the Battle of Baghdad, the Iraqi National Museum was looted consecutively for three days, with thousands of pieces of history systemically stolen. The history of Iraq is extremely old, as it is the site of one of the first civilizations, ancient Mesopotamia. Many of the stolen pieces were thousands of years old and are worth thousands of dollars. 

According to the film \textit{Robbing the Cradle of Civilization}, the ``major players'' in the world's antiquities market are the looters, private collectors, governments, armies, and museums.\footnote{\textit{Robbing the Cradle of Civilization}, directed by Robin Benger (2003; Ottawa, Canada: Canadian Broadcasting Corporation, 2003.), TV.} Looters are the first to interact with items to be brought into the world's antiquities market. Lack of economic growth causes many to turn to less than ideal ways of surviving. In areas with high concentrations of antiquities, slow economic growth or even decline can lead to looting of these items. These items are sold to private collectors, who pay large amounts of money to add antiquities to their exhibits. Private collectors also play a major role in the market, as without them, there would be limited incentive for looters to pillage their own history. Additionally, governments also play a part in the global antiquities trade. For example, in Israel, many stolen Iraqi seals are openly sold in government approved shops.\footnote{\textit{Ibid.}} These activities are sanctioned by the government of Israel, and is an outlet for stolen goods from Iraq and other Middle Eastern countries to the private collectors. In the case of the Iraqi National Museum, the coalition forces were also a player in how the items entered the antiquities market. When the coalition invaded Iraq, it was partly under the guise that they were there to free the Iraqi people. However, upon entering Baghdad, the coalition did not protect the Iraqi National Museum until a week after the looting began. The research director of the museum, Donny George asked American forces to help protect the museum immediately after the looting began, but unfortunately they were unable to help as they did not have the necessary orders.\footnote{\textit{Ibid.}} By the time the orders were given, it was too late as the looting was already over. By creating the conditions for the looting to occur (invading Baghdad), and not protecting the Iraqi National Museum, the coalition forces were also implicit in the addition of Iraqi antiquities to the market. Finally, museums also play a role in the antiquities market due to their ability to ``wash'' the looted status off of items.\footnote{\textit{Ibid.}} While most museums cannot own stolen art, they are able to exhibit private collections, which can contain stolen art. Once stolen art is displayed in a museum, it is perceived as clean by the public.

\newpage
\singlespacing
\begin{center}
{\large\textit{Works Cited}}
\end{center}

\begin{bib}{2em}
``Iraq War 2003-2011.'' \textit{Britannica}. Accessed October 24, 2017. \url{https://www.britannica.com/event/Iraq-War}. \\

\textit{Robbing the Cradle of Civilization}. Directed by Robin Benger. 2003. Ottawa, Canada: Canadian Broadcasting Corporation, 2003. TV.
\end{bib}
\end{document}